\vspace{-2cm}A generative model for urban firm networks

### 2020-09-01 main.tex
Update on Overleaf.

%%%%%%%%%%%%%%
\begin{figure}
    \centering
    \includegraphics{}
    \caption{{\bf Map of network communities obtained by modularity maximisation.}}
    \label{fig:map_communities}
\end{figure}
%%%%%%%%%%%%%%

@@

%\todo{which model is what is not clear between the text and the table / econometric conventions}

%\section*{Results}

@@

We run a specific experiment to study the impact of urban hierarchy on firms dynamics.

@@

When considering optimal points with $\varepsilon_L < 5.0$, the adjusted parameters are: long range gravity interactions and socio-economic interactions given by $d_G = 1/\gamma_G = 5205 \pm 1775$ and $d_D = 1/ \gamma_D = 109 \pm 29$ (the maximal $g_{ij}$ is 11.8); a stronger influence of destination than origin as $\gamma_F = 1.45 \pm 0.09$ and $\gamma_T = 2.0 \pm 0.06$; a comparable influence of sectors as $\gamma_S = 1.75 \pm 0.17$; a fine time granularity as $t_f = 4960 \pm 109$; and a very strong influence of previous links as $\gamma_W = 7.99 \pm 3.77$. This last point furthermore shows in particular a role of the path-dependency parameter, confirming the relevance of this complex generative model including path-dependency. The interaction of this process with others implies an inversion of the relative importance of origin and destination (on the contrary to statistical models). The fact that calibrated interaction distances are large is consistent with long range economic interactions within Europe. Besides these stylized facts, these calibration results altogether demonstrate the feasibility of model application to real data.

>>>>

%%%%%%%%%%%%%%
\begin{figure}
    \begin{center}
    \includegraphics[width=\linewidth]{figures/map_communities_louvain.png}
    \end{center}
    \caption{{\bf Map of network communities obtained by modularity maximisation.} Area of circles gives the population with the Functional Urban Area, and color the community it belongs to. Urban Areas in communities of size smaller than 3 were not colored for readability.}
    \label{fig:map_communities}
\end{figure}
%%%%%%%%%%%%%%

@@

@@

We run a specific experiment to study the impact of urban hierarchy on firms dynamics. Rank-size law in cities is a central stylized fact to urban theories, despite the discussions on how to estimate the power-law exponent, its actual values \cite{cottineau2017metazipf} and how its depends on the definition of cities considered \cite{corral2020truncated}. In that particular context, understanding how this parameter can impact urban dynamics within artificial systems of cities in which it can be modified to extreme values not observed in real systems, should inform on underlying processes. % too abstract: clarify why hypothetical systems of cities bring info on real ones
We change the initial hierarchy $\alpha$ from 0.2 to 2.0 with a step of 0.1, and also vary interaction range $d_0$.

@@

When considering optimal points with $\varepsilon_L < 5.0$, the adjusted parameters are: long range gravity interactions and socio-economic interactions given by $d_0 = 5205 \pm 1775$ and $c_0 = 109 \pm 29$ (the maximal $c_{ij}$ is 11.8); a stronger influence of destination than origin as $\gamma_O = 1.45 \pm 0.09$ and $\gamma_D = 2.0 \pm 0.06$; a comparable influence of sectors as $\gamma_S = 1.75 \pm 0.17$; a fine time granularity as $t_f = 4960 \pm 109$; and a very strong influence of previous links as $\gamma_W = 7.99 \pm 3.77$. This last point furthermore shows in particular a role of the path-dependency parameter, confirming the relevance of this complex generative model including path-dependency. The interaction of this process with others implies an inversion of the relative importance of origin and destination (on the contrary to statistical models). The fact that calibrated interaction distances are large is consistent with long range economic interactions within Europe. Besides these stylized facts, these calibration results altogether demonstrate the feasibility of model application to real data.
